\subsection{Tools and Software}

This study utilized several powerful libraries and tools for data processing, model training, and evaluation:

\begin{itemize}[leftmargin=*]
    \item \textbf{Scikit-learn}: Used for MLP, RF, and metrics such as F1, Balanced Accuracy, Accuracy, MCC, ROC, AUC, permutation importance, train-test split, confusion matrix and voting classifiers.
    \item \textbf{Torchaudio}: Used to load the audio, for MFCC extraction and audio resampling.
    \item \textbf{Librosa}: Used for other features extraction and audio processing and augmentation.
    \item \textbf{Imblearn}: Applied for handling imbalanced datasets with techniques such as undersampling, oversampling, and SMOTEN.
    \item \textbf{Numpy}: Essential for numerical computations and array manipulations.
    \item \textbf{Pandas}: Crucial for data manipulation and analysis.
    \item \textbf{Matplotlib}: Employed for creating visualizations.
    \item \textbf{Seaborn}: Used for statistical data visualization.
    \item \textbf{Scipy}: Utilized for scientific and technical computing.
    \item \textbf{XGBoost}: Implemented for gradient boosting models.
    \item \textbf{CatBoost}: Applied for gradient boosting on decision trees.
    \item \textbf{PyTorch}: Used for developing and training CNN models, specifically VGG16\_bn.
    \item \textbf{TensorFlow}: Used for building and training deep learning models, including CNNs.
    \item \textbf{Keras}: High-level API for building and training neural networks on TensorFlow.
    \item \textbf{Shap}: Utilized for model interpretability.
    \item \textbf{Other Utility Libraries}: Includes \texttt{joblib} for model serialization, and \texttt{os}, \texttt{sys} for system operations and file handling.
\end{itemize}