\documentclass[twocolumn]{class}


\addbibresource{References.bib}

% add path to images
\graphicspath{ {./images/} }

\title{Heart Disease Recognition \\ from heart beat audio signals}
\shorttitle{Heart Disease Prediction}

\github{https://github.com/DavideLigari01/advanced-biomedical-project}

\author{Ligari D. • Alberti A.}
\university{\hspace{1.7cm}Department of Computer Engineering, Data Science, University of Pavia, Italy \newline\centering Course of Advanced Biomedical Machine Learning}
\keywords{ Heartbeat Classification • Machine Learning • Audio Features • Correlation Analysis • Ensemble Models}
\abstract{
   The early detection of heart diseases is crucial for reducing mortality, 
   yet traditional diagnostic methods often fail to identify conditions until advanced 
   stages. Leveraging advancements in machine learning, this study presents two different 
   models aimed at enhancing heart disease detection from heart sound recordings. The models, 
   MLP\_Ensemble5 and MLP\_Ensemble2, were developed using advanced ensemble techniques 
   and optimized to balance computational efficiency with diagnostic accuracy. 
   MLP\_Ensemble5 focuses on minimizing false normals, and MLP\_Ensemble2 emphasizes overall performance 
   and incorporates explainability measures to aid medical professionals. 
   The study utilizes a dataset of heart sound recordings, processed through steps 
   of data preprocessing, feature extraction using several spectral coefficients (MFCCs, Chroma STFT\dots),
   and feature selection to develop robust predictive models. Despite promising 
   results, the research faced limitations such as the small dataset size, leading to potential 
   biases due to lack of a validation set, and challenges in capturing complete cardiac 
   cycles with the chosen extraction intervals. Moreover, the models’ explainability, necessitates further validation. 
   Future work will focus on expanding the dataset, optimizing extraction intervals to 
   capture full cardiac cycles, exploring alternative feature extraction techniques, 
   and enhancing model explainability to ensure clinical applicability. This study 
   demonstrates the potential of machine learning models in heart disease detection 
   and underscores the need for further research to overcome current limitations and 
   enhance model reliability in clinical settings.
}
\firstauthor{Alberti Ligari}
\publicationdate{\today}


\begin{document}

\maketitle
\pagestyle{FirstPage}

\tableofcontents
% \nocite{dizdar_dns_2021}

% ------------------- START OF SECTIONS -------------------


% ------------------- Introduction -------------------

\input{./files/Introduction.tex} % both
\pagestyle{OtherPage}

\section{Methods}
\input{files/Source_of_data.tex} % mix

\input{files/Data_preprocessing.tex} % Andrea

\input{files/Feature_Extraction.tex} % mix

\input{files/Feature_Selection.tex} % Davide

\subsection{Models} % Davide

\input{files/Metric_used.tex} % Davide

\input{files/Prevention_Model_methods.tex} % Andrea

\input{files/Support_Model_methods.tex} % Davide

\input{files/Experimented_Architectures.tex} % Andrea


\input{files/Tools_and_software.tex} % Andrea

\section{Results}
\input{files/Prevention_Model_results.tex} % Andrea

\input{files/Support_Model_results.tex} % Davide

\input{files/Other_experiments.tex} % Andrea

% Section discussion
\input{files/Discussion.tex}

% Section Conclusion
\input{files/Conclusion.tex}

\clearpage
\input{files/appendix.tex}

\clearpage
\printbibliography

\end{document}